---
title: "Linear Model"
author: "Natalia Lekach"
date: "March 24, 2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

You can import the data directly from a link to its website.  Copy that link to the clipboard by right clicking on Raw Data and then copy link.

Then issue
data <- read.csv(file="paste link here",sep="",header=TRUE)  

that sep=""  in the command is needed since the file is space delimited, not comma separated.  The header=TRUE is also necessary so that the names of the variables and their formats get correctly imported.

```{r}
data <- read.csv(file= "https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
```


## Introduction

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
