---
title: "Linear Model"
author: "Natalia Lekach"
date: "March 24, 2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data <- read.csv(file= "https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
```


## Introduction

In this exercise, we will build three regression models and see which one best predicts a person's score on the work simulations. Model1 will use the arm strength test to predict the work simulation score, Model2 will use the grip test, and Model3 will use the sum of the arm and grip tests. 
By completing these linear regression models, and subsequent ANOVAs, we will determine which model best predicts the simulation scores of the test particpants.   

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
