---
title: "Linear Model"
author: "Natalia Lekach"
date: "March 24, 2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
```

```{r}
modeldata<- read.csv(file= "https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
```


## Introduction

In this exercise, we will build three regression models and see which one best predicts a person's score on the work simulations. Model1 will use the arm strength test to predict the work simulation score, Model2 will use the grip test, and Model3 will use the sum of the arm and grip tests. For each model we will find a 95% prediction interval of SIMS, given a value of 94  for GRIP and 88 for ARM.
By completing these linear regression models, and subsequent ANOVAs, we will determine which model best predicts the simulation scores of the test participants.   


# Model 1: SIMS~ARM

## Graphical Results
```{r}
basicNN <- ggplot(modeldata,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point()
```
  
There seems to be a positive relationship between ARM and SIMS. Those with higher ARM test scores, tend to have high SIM scores as well.  

## Numerical results
```{r}
cor(SIMS~ARM,data=modeldata)
```

There is a correlation of 0.686 between the arm test score and the SIMS score.  

## Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=modeldata)
summary.lm(model.1)
newdata<-data.frame(GRIP=94,ARM=88)
predict.lm(model.1,newdata,interval="prediction")
```

##### Model 1 Regression Plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 
  
Using the inferential results, we know the equation for SIMS is SIMS=0.055*ARM-4.095. For Model 1, the adjusted R-squared is 0.467 and the residual stanard error is 1.226.

# Model 2: SIMS~GRIP

## Graphical Results
```{r}
basicGrip <- ggplot(modeldata,aes(y=SIMS,x=GRIP))
```

```{r}
basicGrip + geom_point()
```
  
There seems to be a positive relationship between GRIP and SIMS. Those with higher GRIP test scores, tend to have high SIM scores as well.  

## Numerical results
```{r}
cor(SIMS~GRIP,data=modeldata)
```

There is a correlation of 0.6399 between the grip test score and the SIMS score.  

## Inferential  (Build linear model)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=modeldata)
summary.lm(model.2)
newdata<-data.frame(GRIP=94,ARM=88)
predict.lm(model.2,newdata,interval="prediction")
```

##### Model 2 Regression Plot
  
```{r}
basicGrip + geom_point() + geom_smooth(method=lm)
``` 
  
Using the inferential results, we know the equation for SIMS is SIMS=0.0455*GRIP-4.8097. For Model 2, the adjusted R-squared is 0.4053 and the residual standard error is 1.295.

# Model 3: SIMS~ARM+GRIP
 
## Inferential  (Build linear model)
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=modeldata)
summary.lm(model.3)
newdata<-data.frame(GRIP=94,ARM=88)
predict.lm(model.3,newdata,interval="prediction")
```

Using the inferential results, we know the equation for SIMS is SIMS=0.0373 * ARM + 0.0245 * GRIP-5.434.
The adjusted R-squared for Model 3 is 0.5358 and the residual standard error is 1.144. 

# ANOVA

Model 1 and Model 3 both had higher adjusted r-squared than Model 2. We will compare Model 1 and Model 3 using an ANOVA to determine if ARM or ARM+GRIP is a better model to predict SIMS.  

```{r}
anova(model.1,model.3)
```


